---
title: "My Dazzling Report"
author: "Lindsey Dietz, PhD"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: united
    highlight: tango
    code_folding: hide

---
<!-- (stuff above this line is YAML Ain't Markup Language (YAML) and behaves differently than the rest of the doc) -->


<!-- (this chunk shows up when you create Rmarkdown to show you how to set global options; `echo = FALSE` prevents printing of the R code inside chunks) -->
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
```

<!-- (This statement above all tabs) -->
This is my report for the Management Committee. I'm creating a plot using `ggplot`


<!-- (making tabs) -->
<!-- # header 1, all tabs need to be ## header 2 to nest -->

# {.tabset .tabset-pills}

## Some Info

<!-- (** makes it bold) -->
**This is really important information that people should read before looking at my output.**

Here is a key formula that the reader should know about: $y = \alpha + \beta x$.

References:

<!-- (one type of link) -->
 - Tabs: https://bookdown.org/yihui/rmarkdown-cookbook/html-tabs.html
 - [Using Rmarkdown in your development process](https://rstudio.com/resources/rstudioconf-2020/rmarkdown-driven-development/)

<!-- (another type of link) -->
These are the R packages I'm going to highlight:

<!-- (here is an R code chunk; I've used some options to hide things) -->
```{r libraries1, include = FALSE}
library(dplyr)
library(tidyr)
```

```{r libraries2, echo = TRUE}
#The report
library(rmarkdown)

#Plots
library(ggplot2)
```

I'm going to get some unemployment data from FRED to demo.

```{r, results = 'hide', echo = TRUE}
#' @param start_date string in the form "YYYY-MM-DD"
#' @param end_date string in the form "YYYY-MM-DD"
#' @return data.frame

fred_function <- function(start_date, end_date){
  
  #------- Ensuring dplyr and fredr are loaded -----------------
  library(dplyr)
  library(fredr)
  
  #------ Getting several different unemployment series --------
  df1 <- fredr::fredr(
    series_id = "UNRATE",
    observation_start = as.Date(start_date),
    observation_end = as.Date(end_date)) %>% 
    mutate(series_id = "Total")
  
  df2 <- fredr::fredr(
    series_id = "LNS14000006",
    observation_start = as.Date(start_date),
    observation_end = as.Date(end_date)) %>% 
    mutate(series_id = " Black/African American")
  
  df3 <- fredr::fredr(
    series_id = "LNS14000003",
    observation_start = as.Date(start_date),
    observation_end = as.Date(end_date)) %>% 
    mutate(series_id = " White")
  
  df4 <- fredr::fredr(
    series_id = "LNS14000009",
    observation_start = as.Date(start_date),
    observation_end = as.Date(end_date)) %>% 
    mutate(series_id = " Hispanic/Latino")
  
  
  df <- rbind(df1, df2, df3, df4) %>%
    dplyr::rename(Category = series_id,
                  Date = date,
                  UR = value) %>%
    dplyr::select(-realtime_start, -realtime_end) %>%
    #Adding recession indicators
    dplyr::mutate(recession = ifelse(Date >= '2020-02-01' | 
                                       (Date >= '2007-12-01' & Date < '2009-07-01') | 
                                       (Date >= '2001-03-01' & Date < '2001-12-01'), TRUE, FALSE),
                  quarter_start = ifelse(substr(Date, 6, 7) %in% c('01','04','07','10'), TRUE, FALSE))
  
  #-------- Writing to disk for vintaging ------------------
  write.csv(df, paste0("../data/fred_out_", end_date, ".csv"), row.names = FALSE)
  
  return(df)
  
}

df <- fred_function(start_date = "2005-01-01", end_date = "2021-09-01")
```

## Plot

<!-- (Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.) -->
```{r plot, fig.width=10}

myplot <- ggplot(df, aes(x = Date, y = UR, color = Category)) + 
  geom_line() +
  theme_bw() + ylab("Unemployment Rate")

  #Fixed ggplot
  myplot


```