---
title: "My Dazzling Report"
author: "Lindsey Dietz, PhD"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: united
    highlight: tango
    code_folding: hide
params:
  dept: 'Management Committee'
  plot_type: 
      value: 'highcharter'
      choices: ['highcharter', 'ggplot2', 'plotly']
  data_start_date: '2005-01-01'
  data_end_date: '2021-09-01'

---
<!-- (stuff above this line is YAML Ain't Markup Language (YAML) and behaves differently than the rest of the doc) -->


<!-- (this chunk shows up when you create Rmarkdown to show you how to set global options; `echo = FALSE` prevents printing of the R code inside chunks) -->
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
```

<!-- (using parameters in Rmarkdown; don't forget the r) -->
<!-- (This statement above all tabs) -->
This is my report for the `r paste(params$dept)`. I'm creating a plot using `r paste(params$plot_type)`.  


<!-- (making tabs) -->
<!-- # header 1, all tabs need to be ## header 2 to nest -->

# {.tabset .tabset-pills}

## Some Info

<!-- (** makes it bold) -->
**This is really important information that people should read before looking at my output.**

Here is a key formula that the reader should know about: $y = \alpha + \beta x$.

References:

<!-- (one type of link) -->
 - Tabs: https://bookdown.org/yihui/rmarkdown-cookbook/html-tabs.html
 - [Using Rmarkdown in your development process](https://rstudio.com/resources/rstudioconf-2020/rmarkdown-driven-development/)

<!-- (another type of link) -->
These are the R packages I'm going to highlight:

<!-- (here is an R code chunk; I've used some options to hide things) -->
```{r libraries1, include = FALSE}
library(dplyr)
library(tidyr)
```

```{r libraries2, echo = TRUE}
#The report
library(rmarkdown)

#Plots
library(ggplot2)
library(plotly)
library(highcharter)
```

I'm going to get some unemployment data from FRED to demo.

```{r, results = 'hide', echo = TRUE}
source("../scripts/fred_script.R")
df <- fred_function(start_date = params$data_start_date, end_date = params$data_end_date)
```

## Interactive or Fixed Plot

<!-- (Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.) -->
```{r plot, fig.width=10}

myplot <- ggplot(df, aes(x = Date, y = UR, color = Category)) + 
  geom_line() +
  theme_bw() + ylab("Unemployment Rate")

if(params$plot_type == 'plotly'){
  #Dynamic plot with plotly 
  ggplotly(myplot)
  
}else if (params$plot_type == 'highcharter'){
  
 #Dynamic plot with highcharter
 df %>% 
    dplyr::select(Date, Category, UR)  %>% 
    highcharter::hchart(., 
         type = "line", 
         hcaes(x = Date, 
               y = UR, 
               group = Category)) %>% 
  hc_yAxis(opposite = TRUE,
           labels = list(format = "{value}%")) %>% 
  hc_tooltip(pointFormat = '{point.x:%Y-%m-%d}')
  
}else if (params$plot_type == 'ggplot2'){
  #Fixed ggplot
  myplot
}

```