---
title: "My Dazzling Report"
author: "Lindsey Dietz, PhD"
date: "`r Sys.Date()`"
output: pdf_document
params:
  dept: 'Management Committee'
  data_end_date: '2021-09-01'

---
<!-- (stuff above this line is YAML and behaves differently than the rest of the doc) -->


<!-- (this just shows up when you create Rmarkdown) -->
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- (using parameters in Rmarkdown; don't forget the r) -->
This is my report for the `r paste(params$dept)`. 


<!-- (making sections) -->

## Some Info

<!-- (** makes it bold) -->
**This is really important information that people should read before looking at my output.**

Here is a key formula that the reader should know about: $y = \alpha + \beta x$.

References:

<!-- (one type of link) -->
 - Tabs: https://bookdown.org/yihui/rmarkdown-cookbook/html-tabs.html
 - [Using Rmarkdown in your development process](https://rstudio.com/resources/rstudioconf-2020/rmarkdown-driven-development/)

<!-- (another type of link) -->
These are the R packages I'm going to highlight:

<!-- (here is an R code chunk; I've used some options to hide things) -->
```{r libraries1, warning = FALSE, include = FALSE, message = FALSE}
library(dplyr)
library(tidyr)
```

```{r libraries2, warning = FALSE, message = FALSE}
#The report
library(rmarkdown)

#Tables
library(kableExtra)

#Plots
library(ggplot2)
```

I'm going to get some unemployment data from FRED to demo but I'm hiding my code from you.

```{r, results = 'hide', echo=FALSE, message = FALSE}
source("../scripts/fred_script.R")
start_date <- "2005-01-01"
end_date <- params$data_end_date
analyst_info <- data.frame(start_date, end_date, date_executed = Sys.Date())
df <- fred_function(start_date = start_date, end_date = end_date)
```

<details>
<summary> Analysts might want to know this information. </summary>
```{r, message = FALSE}
print(analyst_info)
```
</details>

## Fixed Tables

### with kableExtra

["The goal of kableExtra is to help you build common complex tables and manipulate table styles. It imports the pipe %>% symbol from magrittr and verbalize all the functions, so basically you can add “layers” to a kable output in a way that is similar with ggplot2 and plotly." -- Hao Zhu](https://haozhu233.github.io/kableExtra/)



```{r fred_table, echo=FALSE}
df %>%
  dplyr::filter(recession == TRUE & quarter_start == TRUE) %>%
  dplyr::select(Category, Date, UR) %>%
  dplyr::mutate(UR = kableExtra::cell_spec(UR,  "latex", color = 'white', background = kableExtra::spec_color(UR, begin = 0.3, end = 0.8, direction = -1, alpha = 0.5, option = 'B'))) %>%
  knitr::kable(caption = "Recession Unemployment Rates by Demographic", escape = F, align = "llr") %>%
  kableExtra::collapse_rows(columns = 1) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position")) %>%
  kableExtra::kable_paper()

```

## Fixed Plot

<!-- (Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.) -->
```{r plot, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10}

myplot <- ggplot(df, aes(x = Date, y = UR, color = Category)) + 
  geom_line() +
  theme_bw() + ylab("Unemployment Rate")

#Fixed ggplot
myplot

```